### 2014-03-02 paper/intro.tex
More intro stuff
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

Information flow control (IFC) is a promising technique to enforce
security policies by tracking the flow of sensitive data through
a system.  The idea is to prevent the leaking of secret or sensitive
data into public channels by enforcing the notion of non-interference.
Significant research has been devoted to adding various
forms of IFC to different kinds of programming languages and system,
both static and dynamic in nature.  In this paper we are interested
in the latter, where an execution monitor ensure at runtime that secret
information is not revealed through public outputs.
A key challenge in the design of these dynamic systems has been the
performance cost incurred by additional security checks.
Particularly when retrofitting an existing programming language with
IFC it is tempting to track information flow at a fine-grained level,
e.g., per value in the system.  This can lead to impractical
runtime overheads even for ordinary operations.

>>>>

A defining aspect of web platforms is the combinability of many
components of various providence.  This pattern shows up in browser
extensions, which run JavaScript code alongside third-party website
code, web applications, which include possibly untrusted third-party
libraries, and mash-up websites, which combine code and data from
websites which may not even be aware of each other's existence.  While
this combinability has offered great flexibility, it also poses a set of
unique security challenges: in particular, maintaining the privacy of
data in these settings is difficult, if not impossible.

Information flow control (IFC) is a promising technique for addressing these
problems, by tracking the flow of sensitive data through a system and
confining untrusted code so that it cannot exfiltrate data, except as
per a information flow policy.  Significant research has been devoted to
adding various forms of IFC to different kinds of programming languages
and systems.  In the context of the web, however, there is a strong
motivation to preserve the language JavaScript, and retrofit information
flow control on top of it.  A key challenge in the design of these
systems is ensuring they can be implemented efficiently: when the
semantics specify that information flow must be tracked at a
fine-grained level, e.g., per value in the system,  it can lead to
impractical runtime overheads even for ordinary operations.
